Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-05-28 Manuscript.Rmd
fixed figure and tiny data measurement error (1 decision RT off by 2s in 1 subj)

  Next, we tested the hypothesis that foragers would exhibit within-trial consistency and across-trial stability in their choices. Participants were deemed consistent if they did not quit after engaging in a trial. To examine this, we plotted survival curves of trial quits across all participants (Fig. 4, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels. These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit afterwards (percentage of quits after 1 s = `r  handlingQuits_btw$r * 100`). Physical and easy groups showed slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line). This resulted in some individuals opting to wait for that second to indicate an offer rejection (the censor at 4s in the physical group was a completion during a 2 s handling trial that was incorrectly recorded as 4 s by the experimental code). Plotting the quitting time distributions across blocks for the first second of the handling time (ECDFs on Fig. 4, top-right) showed that participants in the wait and cognitive groups responded faster as the experiment progressed. These response time observations suggested clarity in participant choices.

```{r Survival and prepost plots (Fig. 4), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1. Top: Survival curve (left), and distribution of times when participants quit a trial over time (right). Bottom: Proportion accepted in the second half as a function of first half acceptances (left). Dashed lines indicate the mean for each group. On the right, the proportion accepted over time per group. The order of blocks was repeated in the second half (indicated by the black dashed line)."}
# plots generated in 16.3.1. and 16.3.2.
# historyPlot_btw <- (suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks)
# ggsave("./Images/FIG5_survival.png", historyPlot_btw, device = "png", height = 8, width = 10)
include_graphics("./Images/FIG4_survivalbtw.png")
```

>>>>

  Next, we tested the hypothesis that foragers would exhibit within-trial consistency and across-trial stability in their choices. Participants were deemed consistent if they did not quit after engaging in a trial. To examine this, we plotted survival curves of trial quits across all participants (Fig. 4, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels. These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit afterwards (percentage of quits after 1 s = `r  handlingQuits_btw$r * 100`). Physical and easy groups showed slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line). This resulted in some individuals opting to wait for that second to indicate an offer rejection. Plotting the quitting time distributions across blocks for the first second of the handling time (ECDFs on Fig. 4, top-right) showed that participants in the wait and cognitive groups responded faster as the experiment progressed. These response time observations suggested clarity in participant choices.

```{r Survival and prepost plots (Fig. 4), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1. Top: Survival curve (left), and distribution of times when participants quit a trial over time (right). Bottom: Proportion accepted in the second half as a function of first half acceptances (left). Dashed lines indicate the mean for each group. On the right, the proportion accepted over time per group. The order of blocks was repeated in the second half (indicated by the black dashed line)."}
# individual plots generated in 16.3.1. and 16.3.2.
# to recreate the combined plot and save it:
# historyPlot_btw <- (suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks)
# ggsave("./Images/FIG5_survival.png", historyPlot_btw, device = "png", height = 8, width = 10)
include_graphics("./Images/FIG4_survivalbtw.png")
```
